\section{Related Work}
\label{sec:related}

\subsection{Scene and handwritten text detection}
Segmentation-based detectors dominate the modern arbitrarily-shaped
text detection literature. PSENet~\cite{wang2019pse} predicts
progressively shrunken text kernels and expands them at inference to
recover instance boundaries, yielding robustness to curved and
closely-spaced text. DBNet~\cite{liao2020real} introduces a
differentiable binarization head that allows the threshold map to be
learned end-to-end with the probability map, making the
binarisation-and-contour pipeline fully trainable and substantially
faster than prior shrink--expand variants. DBNet++~\cite{liao2022dbpp}
adds an adaptive scale-fusion module on top of DBNet and remains the
strongest segmentation-based baseline on standard scene benchmarks.
FCENet~\cite{zhu2021fcenet} takes a complementary contour-regression
view, embedding text instance contours as Fourier signatures and
decoding them directly. In this work we adopt DBNet with a ResNet-18
backbone as the detection scaffold: its lightweight footprint matches
our MPS-only training budget, its segmentation output is directly
consumable by the EMA teacher described in
Sec.~\ref{sec:method:uda}, and its avoidance of deformable
convolutions side-steps the operators that are unsupported on the
Apple Silicon backend. Handwritten-document detection introduces its
own challenges (column layouts, ink bleed-through, marginalia), which
recent Mongolian-specific work has begun to address; we discuss the
most relevant Mongolian baselines below.

\subsection{Unsupervised domain adaptation for OCR}
Unsupervised domain adaptation for visual recognition splits broadly
into feature-alignment and self-training families. The
feature-alignment line begins with DANN~\cite{ganin2015dann}, which
attaches a domain classifier to the feature extractor through a
gradient-reversal layer, encouraging features to be domain-invariant.
DANN-style alignment is now a standard component of cross-domain
detection pipelines. The self-training line uses pseudo-labels
produced by an EMA teacher on the unlabeled target domain to
supervise the student; Cross-Domain Adaptive Teacher
(AT)~\cite{li2022adapttch} demonstrated that combining
teacher--student pseudo-labelling with image-level adversarial
alignment substantially closes the source-to-target gap on object
detection benchmarks, and MIC~\cite{hoyer2023mic} further showed that
masked-image consistency can suppress the teacher--student drift that
long-schedule self-training tends to develop.

Most UDA-detection studies, however, evaluate on benchmarks where
the source-only model already produces non-trivial target output
(e.g.\ Cityscapes\,$\to$\,Foggy Cityscapes, Sim10k\,$\to$\,Cityscapes),
so the pseudo-label loop has a reasonable starting point. Our
setting differs in two key ways. First, one of the two cross-domain
directions we study has zero source-only true positives -- a true
cold-start condition in which the teacher cannot bootstrap by
itself. Second, the corpus is small ($\sim$1k--1.5k images per
domain) and the compute budget is constrained to a single
Apple-Silicon device, which collectively rule out the long training
schedules and heavy backbones common in UDA-detection work. These
conditions surface failure modes that the prevailing recipe does not
address, motivating the cold-start fix and conservative weighting we
propose.

\subsection{Mongolian and bilingual Mongolian--Chinese text detection}
Mongolian text detection has only recently received dedicated
attention. Liu et al.~\cite{liu2025tcdrr} introduce TCDRR, a text
clarification and deep relational reasoning detector for
Mongolian--Chinese bilingual arbitrary-shaped scene text, evaluated
on a custom bilingual scene benchmark, reporting an in-domain
$F_1$ of $84.6\%$. Ding et al.~\cite{ding2026contour} address
handwritten Mongolian archival documents with a contour-thinning
detector that iteratively refines candidate text boundaries to
handle marginalia and ink bleed-through, achieving an in-domain
$F_1$ of $99.0\%$ on a self-collected benchmark.

Both works tackle each domain in isolation; neither addresses the
cross-domain transfer problem, and neither uses target-domain
unsupervised adaptation. The present paper complements this line by
reusing the same two domains as cross-domain endpoints, taking the
in-domain detectors of~\cite{liu2025tcdrr,ding2026contour} as oracle
upper bounds, and asking how well a single detector can be made to
perform on the \emph{other} domain without target annotations. To the
best of our knowledge, this is the first systematic cross-domain UDA
study on a Mongolian text-detection benchmark.

\subsection{Positioning}
Compared to prior UDA-OCR work, our problem has two distinguishing properties:
(i) one of the two cross-domain directions has a true zero source-only
baseline (no detections at any threshold), creating an extreme cold-start
condition; and (ii) the corpus is small and the compute budget is constrained
to a single Apple-Silicon (MPS) device, ruling out long schedules and
heavy backbones. These properties expose failure modes (Sec.~\ref{sec:method})
and motivate the conservative training schedule we adopt
(Sec.~\ref{sec:exp}).
