\section{Experiments}
\label{sec:exp}

\subsection{Datasets and splits}
\label{sec:exp:data}
\TODO{Document handwriting (1003 images, 20{,}115 polygons) and scene
(1502 images, 18{,}598 polygons), training/val/test split ratios,
and the polygon vs.\ quadrilateral distribution. Include a small
illustrative figure (one tile per domain).}

\subsection{Implementation details}
\label{sec:exp:impl}
\TODO{Hardware (Apple M5 Pro, MPS), framework (PyTorch nightly),
optimiser (AdamW, lr 1e-4), batch size, augmentation, training/eval
thresholds, total walltime per run.}

\subsection{Cross-domain motivation: oracle vs.\ source-only}
\label{sec:exp:motivation}

\TODO{Insert reproduction of Stage-1 motivation table from
\texttt{baseline\_results.md}: scene oracle = 0.385 in-domain $\hmean$;
handwriting oracle = 0.863; cross-domain $\hsource$ source-only = 0.059;
$\stoh$ source-only = 0.000. Emphasise that $\stoh$ source-only produces
zero true positives at every post-process threshold, motivating the
cold-start fix discussed in Sec.~\ref{sec:method:coldstart}.}

\begin{table}[t]
\centering
\caption{Cross-domain motivation. In-domain numbers (oracle) and
cross-domain source-only numbers on the test split, all at the matched
post-process thresholds (\texttt{box-thresh}=0.45, \texttt{min-score}=0.5).}
\label{tab:motivation}
\begin{tabular}{lcc}
\toprule
Setting & In-domain $\hmean$ & Cross-domain $\hmean$ \\
\midrule
Handwriting oracle ($\hsource$) & 0.863 & 0.0592 \\
Scene oracle      ($\stoh$)     & 0.385 & 0.0000 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Main UDA results}
\label{sec:exp:main}

\TODO{Insert main results table covering both directions, fixed-thresh
and swept-thresh columns, source-only vs.\ UDA, with $\Delta$ in pp.
Numbers are fully captured in baseline\_results.md.}

\begin{table*}[t]
\centering
\caption{Main UDA results on the target test split. $\Delta$ is the
absolute improvement of UDA over source-only at the same threshold
configuration. Bold entries are the per-direction best.}
\label{tab:main}
\begin{tabular}{lcc cc cc}
\toprule
& \multicolumn{2}{c}{\textbf{Fixed thresh (0.45/0.5)}}
& \multicolumn{2}{c}{\textbf{Swept best}}
& \multicolumn{2}{c}{\textbf{$\Delta$ (pp)}} \\
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}
Direction & Source-only & UDA & Source-only & UDA & fixed & swept \\
\midrule
$\hsource$ & 0.0592 & 0.0626 & 0.0753 & \textbf{0.0767} & $+0.34$ & $+0.14$ \\
$\stoh$    & 0.0000 & 0.0285 & 0.0028 & \textbf{0.0654} & $+2.85$ & $\mathbf{+6.26}$ \\
\bottomrule
\end{tabular}
\end{table*}

\subsection{Asymmetric UDA gain analysis}
\label{sec:exp:asym}
\TODO{Discuss why $\stoh$ benefits dramatically and $\hsource$ barely
moves once thresholds are swept on both sides. Two factors:
(i) the source-only model on $\hsource$ already captures enough generic
text-edge signal that threshold sweeping recovers most of the achievable
$\hmean$; (ii) the $\stoh$ source-only model truly produces nothing,
so any non-trivial detection capability must originate from the UDA
self-training process, which in turn is unlocked by the cold-start fix.
This reframes UDA's role: not as a uniform booster, but as a recovery
mechanism for structurally broken transfer directions.}

\subsection{Long-training analysis}
\label{sec:exp:long}
\TODO{Show the 25-epoch curve for $\hsource$ (best $\hmean = 0.0596$ at
ep 3, collapses to $\sim$0.005 by ep 18). Show the 25-epoch curve for
$\stoh$ (best $\hmean = 0.0353$ at ep 1, collapses to $\sim$0 by ep 8,
remains zero through ep 25). Plot both as a single figure. Argue that
the 5-epoch sweet spot is structural, not a budget artefact.}

\subsection{Hyperparameter ablation}
\label{sec:exp:ablation}
\TODO{Present v1 (pseudo-weight-max 0.5, score 0.55), v2 (0.2, 0.7),
v3 (0.1, 0.55) on $\hsource$; argue that v3 best matches v1 best with
much milder late-epoch degradation, and that v2's stricter score
threshold disables the pseudo-label signal entirely by ep 5.}

\subsection{Qualitative results}
\label{sec:exp:qual}
\TODO{Insert the two main comparison figures from
\texttt{docs/figures/}: one for $\hsource$, one for $\stoh$ at the
swept-best thresholds. Each figure shows six rows of the same target
image, source-only on top, UDA below, with input/GT/heatmap/pred
panels. Highlight $\stoh$ where source-only has $\texttt{pred}(0)$ and
UDA recovers visible text columns.}
